The Folly of Passwords

### 2014-12-13 paper.tex
Fixed citations.

Their work is still widely cited 15 years later, but
today, employees are increasingly using passwords in their
workplace in addition to a plethora of passwords for
other services used personally outside of work.
A user-centric design
approach to a modern, enterprise security setup needs to
be even more sympathetic to the large burden on users
from managing so many online accounts.

@@

Additionally, SOMEONE explored economic arguments and models
to argue that the incredibly low, \emph{a priori} likelihood
of a user's account being compromised leads to a monetary
cost value far lower than that needed to justify a user
spending any real time at all strengthening their password.
This may be a case for a general, public account, but perhaps
some accounts with, e.g. corporate webmail, could be classed
as higher risk and bigger targets for attackers. An attack
on a corporate account might allow access to systems that
can lead to real economic or reputational damage.

We can argue that these costs -- even if higher than those
in SOMEONE's models -- are mainly suffered by the \emph{organisation}
more than the employees. This is very similar to SOMEONE's
arguments that even in the case of banks, they are likely
to take on the costs of fraud and prevent their customers
from exposure to those costs themselves.

This effect is classed
by SOMEONE as a negative externality on computer users in
that they are taking on additional effort to cover costs
that are not their own. These economic arguments can be
used to make a case for organisations taking more
responsibility and investing more to prevent the costs
from a security compromise. This can be combined with
the arguments for a more user-centric design
\parencite{adams1999users} to build a case for a new
authentication paradigm that is low friction to users and
where economic incentives lead to an equilibrium where
organisations spend exactly as much on security as
is rationally justified by their real risks and costs.

\cite{beautement2009compliance} introduce the idea of a
``compliance budget'' which models how users perceive these costs
and benefits. Their work suggests a cap on the effectiveness of any
security measures within an organisation, but also introduces management
approaches to raise the threshold above which a user will no longer
comply with security policies. This arguably increases the cost-benefit
ratio by making it more worthwhile for users to practice secure
behaviour (even if by increasing sanctions such that avoidance thereof becomes
more beneficial than working around costs from complying with security
requirements). They still admit there is a finite limit to improvements to
this compliance budget through management, training and cultural changes.
This supports the idea that many of the costs simply must be moved to the
organisation itself.

@@

Password-protected accounts are vunerable to at least three
classes of attack\parencite{florencio2014password}:

@@

\cite{florencio2007large} noted that strong passwords are just
as easily stolen through phishing and key logging as weak
passwords. Password strength is thus limited in only protecting
brute force attacks and not problems where users accidentally
or deliberately disclose their password.

@@

Another, softer approach is to attempt to educate users
on choosing strong, yet memorable, passwords. This belief
that weak passwords are always down to lack of training
is fundementally challenged in the influential findings
of \cite{adams1999users}. Their work combined with the
economics-based arguments and models introduced by %WHO?
builds a large weight of evidence that well-informed
users will still not follow much security advice
(sometimes rationally so) to reduce their own costs in
time and effort or to remove a significant barrier
to performing their work tasks.

@@

\cite{adams1999users} note that password expiry increases
the burden on users having to memorise multiple passwords and that
50\% of users in their study wrote passwords down, with one
person citing a monthly password expiration policy as the cause
of having to do so.

\cite{zhang2010security} go further to demonstrate the ease of
algorithmically predicting a user's new password when the old,
expired password is known. They assert that password expiration
is weak at achieving the intent behind its implementation and
support the idea of moving away from passwords entirely.

@@

\cite{preibusch2010password} showed how the pressure to reuse passwords
presents negative externalities from security-indifferent websites upon
security-concerned websites. This presents an organisation with
security risks stemming solely from the existence of other, less
secure websites with which its employees have accounts.

@@

\cite{van2011tiqr} introduced a new alternative authentication mechanism
called \emph{tiqr} that uses QR codes and a bespoke smartphone app. In
doing so, he also listed and evaluated a number of existing alternatives. We
can thus make a working list of existing non-password authentication
mechanisms:

@@

Given the wide variety of
options for integrating with services such as email, we did not go as far
as to evaluate them all and a thorough examination of a smartcard-based,
enterprise computer network is a subject for further research. The most
subtantial work in this area (that we know of) is from \cite{grossesecuring}.
This research compares different smartcard technologies and software projects
and evaluates them for functionality that overlaps with the enterprise
requirements we are following in this paper. The information seems to be
quite dated now, 8 years later, as we have mentioned projects in this
section that cover functionality claimed not to exist -- especially for OpenPGP
cards.

>>>>

@@

Additionally, Herley explored economic arguments
and models
to argue that the incredibly low, \emph{a priori} likelihood
of a user's account being compromised leads to a monetary
cost value far lower than that needed to justify a user
spending any real time at all strengthening their password.
This may be a case for a general, public account, but perhaps
some accounts with, e.g. corporate webmail, could be classed
as higher risk and bigger targets for attackers. An attack
on a corporate account might allow access to systems that
can lead to real economic or reputational damage.

We can argue that these costs
are mainly suffered by the \emph{organisation}
more than the employees. This is very similar Herley's
arguments that even in the case of banks, they are likely
to take on the costs of fraud and prevent their customers
from exposure to those costs themselves.

This effect is classed
by Herley as a negative externality on computer users in
that they are taking on additional effort to cover costs
that are not their own. These economic arguments can be
used to make a case for organisations taking more
responsibility and investing more to prevent the costs
from a security compromise. This can be combined with
the arguments for a more user-centric design
\parencite{adams1999users} to build a case for a new
authentication paradigm that is low friction to users and
where economic incentives lead to an equilibrium where
organisations spend exactly as much on security as
is rationally justified by their real risks and costs.

\cite{beautement2009compliance} introduced the idea of a
``compliance budget'' which models how users perceive these costs
and benefits. Their work suggests a cap on the effectiveness of any
security measures within an organisation, but also introduces management
approaches to raise the threshold above which a user will no longer
comply with security policies. This arguably increases the cost-benefit
ratio by making it more worthwhile for users to practice secure
behaviour (even if by increasing sanctions such that avoidance thereof becomes
more beneficial than working around costs from complying with security
requirements). They still admit there is a finite limit to improvements to
this compliance budget through management, training and cultural changes.
This supports the idea that many of the costs simply must be moved to the
organisation itself.

@@

Password-protected accounts are vunerable to at least three
classes of attack \parencite{florencio2014password}:

@@

\textcite{florencio2007large} noted that strong passwords are just
as easily stolen through phishing and key logging as weak
passwords. Password strength is thus limited in only protecting
brute force attacks and not problems where users accidentally
or deliberately disclose their password.

@@

Another, softer approach is to attempt to educate users
on choosing strong, yet memorable, passwords. This belief
that weak passwords are always down to lack of training
is fundementally challenged in the influential findings
of \textcite{adams1999users}. Their work combined with the
economics-based arguments and models introduced by %WHO?
builds a large weight of evidence that well-informed
users will still not follow much security advice
(sometimes rationally so) to reduce their own costs in
time and effort or to remove a significant barrier
to performing their work tasks.

@@

\textcite{adams1999users} note that password expiry increases
the burden on users having to memorise multiple passwords and that
50\% of users in their study wrote passwords down, with one
person citing a monthly password expiration policy as the cause
of having to do so.

\textcite{zhang2010security} go further to demonstrate the ease of
algorithmically predicting a user's new password when the old,
expired password is known. They assert that password expiration
is weak at achieving the intent behind its implementation and
support the idea of moving away from passwords entirely.

@@

\textcite{preibusch2010password} showed how the pressure to reuse passwords
presents negative externalities from security-indifferent websites upon
security-concerned websites. This presents an organisation with
security risks stemming solely from the existence of other, less
secure websites with which its employees have accounts.

@@

\textcite{van2011tiqr} introduced a new alternative authentication mechanism
called \emph{tiqr} that uses QR codes and a bespoke smartphone app. In
doing so, he also listed and evaluated a number of existing alternatives. We
can thus make a working list of existing non-password authentication
mechanisms:

@@

Given the wide variety of
options for integrating with services such as email, we did not go as far
as to evaluate them all and a thorough examination of a smartcard-based,
enterprise computer network is a subject for further research. The most
subtantial work in this area (that we know of) is from \textcite{grossesecuring}.
This research compares different smartcard technologies and software projects
and evaluates them for functionality that overlaps with the enterprise
requirements we are following in this paper. The information seems to be
quite dated now, 8 years later, as we have mentioned projects in this
section that cover functionality claimed not to exist -- especially for OpenPGP
cards.
